\documentclass[letterpaper,11pt]{article}
\usepackage[acronym]{glossaries}
\include{acros}
\usepackage{graphicx}
\usepackage{subfigure}
\graphicspath{ {images/} }
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{minted}
\usepackage{tcolorbox}
\usepackage[margin=1in]{geometry}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{indentfirst}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\renewcommand{\arraystretch}{1.2}
\linespread{1.3}


\begin{document}
%
\title{Implementing the Spalart-Allmaras Turbulence Model in Moltres for Flow Modeling of the
Molten Chloride Fast Reactor}
\author{Sun Myung Park, Madicken Munk\\University of Illinois Urbana-Champaign}
\date{\today}
%
\maketitle
%
\section*{Project Description}

In fluid dynamics, turbulent flow is characterized by unsteady, irregular, and chaotic changes in
flow velocity as opposed to neat, parallel flow layers in laminar flow. Turbulent flows in
\glspl{MSR} induce significant turbulent diffusion effects on heat transfer and \gls{DNP} drift.
The resulting temperature and \gls{DNP} distributions strongly influence the neutron flux through
strong temperature reactivity feedback and delayed neutron emission in different neutron importance
regions \cite{pazsit_5_2017}, respectively. Flow separation and recirculation zones may also occur
in \gls{MSR} designs with significant wall curvature \cite{fiorina_modelling_2014}. Temperature
hotspots occurring in recirculation zones may induce thermal stresses on nearby structural
components and cause temperature-induced reactivity effects. In particular, the TerraPower
\gls{MCFR} design will experience significant turbulent flow owing to its
pool-type \gls{MSR} design. When modeling the \gls{MCFR}, we require a turbulence model to
accurately model turbulent effects and associated multiphysics interactions. Otherwise, flow
modeling in coupled neutronics and thermal-hydraulics simulations of the \gls{MCFR} will be limited
to laminar flow. These simulations with laminar flow modeling will likely fail to capture the true
behavior of the \gls{MCFR} in steady-state operation and in transient accident scenarios.

Moltres is the \gls{MSR} simulation tool currently employed for accident evaluation of the
\gls{MCFR} in NEUP Project 21-24037. However, Moltres does not currently have turbulence modeling
capability for simulating turbulent flows in \glspl{MSR}. Without a turbulence model, the
\gls{MCFR} safety analysis will be restricted by the limitations described above. Therefore, we
propose implementing the \gls{SA} model, a one-equation turbulence model,
in Moltres to address this issue. Since Moltres is built on the \gls{MOOSE} framework
\cite{lindsay_20_2022}, we can
leverage the advanced and developer-friendly features in \gls{MOOSE} to implement a \gls{SA} model
that is highly scalable and compatible with the existing fluid dynamics modeling infrastructure in
\gls{MOOSE}. Once implemented, we will verify the model against published data for the
backward-facing step flow \cite{chen_review_2018}, a common reference problem for separated flow.
The verification and subsequent demonstration of the \gls{SA} model for turbulent flow modeling in
a pool-type \gls{MSR} model similar to the \gls{MCFR} will be submitted to the ANS Winter Meeting
2023. After completing these tasks, we will provide technical support to our NEUP project
collaborators for modeling turbulent flow in their accident evaluation of the \gls{MCFR}. Table
\ref{tab:task} lists the tasks, due dates, and deliverables for this proposal.

\begin{table*}[h]
  \centering
  \footnotesize
  \caption{Tasks, due dates, and deliverables relating to the implementation of the \gls{SA} model
  in Moltres and its subsequent use for coupled neutronics/thermal-hydraulics modeling of the
  \gls{MCFR}. All dates are in the year 2023.}
  \begin{tabular}{l l l}
    \toprule
    \textbf{Tasks} & \textbf{Due Dates} & \textbf{Deliverables}\\
    \midrule
    \gls{SA} model implementation in Moltres & April 30 & - \\
    Documentation and testing of the model & May 15 & Official release of \gls{SA} model
    in Moltres \\
    Model verification for backward-facing step flow & May 30 & Model verification results \\
    Model demonstration in a pool-type \gls{MSR} design & June 15 & Model demonstration results \\
    Submission for the ANS Winter Meeting 2023 & June 26 & Conference paper submission\\
    Moltres technical support for NEUP project collaborators & - & - \\
    \bottomrule
  \end{tabular}
  \label{tab:task}
\end{table*}

{
\footnotesize
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
}

\end{document}
